\vspace{-0.5in}{\bfseries\scshape Transfer Learning for computationally limited training of Vision Transformers on art classification tasks } \\ \vspace{1ex} \normalsize{Bachelor's Project Thesis}\vspace{-2ex}

### 2022-06-08 writing/report.tex
Just went further with writing the introduction. Randomly pushing it now because haven't done that for some time..
At the point where all preliminaries are explained (CNNs, ViTs, TL). Up next: related work and description of current research
Still have to give it a final read, but seems like my first draft is done now..
Working on qualitative analysis now
Added all graphics I have currently to the paper. Qualitative analysis results still need to be included.

\title{\vspace{-0.5in}{\bfseries\scshape 
    Transfer Learning Using Vision Transformers Project (No Title Yet)
    } \\ 
    \vspace{1ex} 
    \normalsize{Bachelor's Project Thesis}\vspace{-2ex}
}

\author{
    \normalsize{Vincent Tonkes, s3617157, v.tonkes@student.rug.nl,} \\ 
    \normalsize{Supervisor: Dr M. Sabatelli}
}

@@

\input{tex/draft_introduction.tex}

\bibliographystyle{plainnat}
\bibliography{literature}

>>>>

\title{\vspace{-0.5in}{\bfseries\scshape 
    Transfer Learning for computationally limited training of Vision Transformers on art classification tasks
    } \\ 
    \vspace{1ex} 
    \normalsize{Bachelor's Project Thesis}\vspace{-2ex}
}

\author{
    \normalsize{V. Tonkes, s3617157, v.tonkes@student.rug.nl,} \\ 
    \normalsize{Supervisor: Dr. M. Sabatelli}
}

@@

\input{tex/draft_introduction.tex}
\input{tex/draft_methods.tex}
\input{tex/draft_results.tex}

\bibliographystyle{apacite}
\bibliography{literature}

### 2022-06-08 writing/tex/draft_methods.tex
Added all graphics I have currently to the paper. Qualitative analysis results still need to be included.

% Experiments build upon Sabatelli et al.

\subsection{Dataset}
% Mention the challenges and show the table, of course. Also add max and min classes per category to the table maybe
% Don't forget to tell that images get scaled and cropped to 224 * 224 size and imagenet normalized
% Dataset described in more detail in Appendix A, including histograms and confusion matrices + balancing 'algorithm'

>>>>

% Experiments build upon Sabatelli et al.
Most of the experiments and analysis discussed below build upon the work done in \citeauthor{sabatelli2018deep} (\citeyear{sabatelli2018deep}).

\subsection{Dataset}
% Mention the challenges and show the table, of course. Also add max and min classes per category to the table maybe
% Don't forget to tell that images get scaled and cropped to 224 * 224 size and imagenet normalised
% Dataset described in more detail in Appendix A, including histograms and confusion matrices + balancing 'algorithm'

\begin{table*}[tb]
\centering
\small
\begin{tabular}{lllll}
\hline
\textbf{Task} & \textbf{\# Samples} & \textbf{\# Classes} & \textbf{Gini coefficient} & \textbf{Sample overlap} \\ \hline
Type classification & 9607 (77628) & 30 (801) & 0.466 (0.974) & 0.686 \\
Material classification & 7788 (96583) & 30 (136) & 0.563 (0.980) & 0.798 \\
Artist classification & 6530 (38296) & 30 (8592) & 0.236 (0.676) & 1 \\
Scaling experiment & 7926 (77628) & 15 (801) & 0.300 (0.974) & - \\ \hline
\end{tabular}
\caption{Overview of the used datasets. Values between brackets show the situation before balancing operations were performed. `Sample overlap' gives the average overlap between 2 of the 5 randomly generated sets per task ($i$ and $j$ where $i \neq j$).}
\label{methods:datasets}
\end{table*}
